Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-09-24 paper/paper.Rmd
corrected affiliations

---
documentclass: jss
author:
  - name: Patrick Schratz
    affiliation: 'Friedrich Schiller University Jena'
    # affiliaton2: 'Ludwig-Maximilians-University Munich'
    # use this syntax to add text on several lines
    address: |
      | Department of Geography
      | Geographic Information Science group
    email: \email{patrick.schratz@uni-jena.de}
  - name: Alexander Brenning
    affiliation: 'Friedrich Schiller University Jena \AND'
    address: |
      | Department of Geography
      | Geographic Information Science group
    email: \email{alexander.brenning@uni-jena.de}
  - name: Marc Becker
    affiliation: 'Ludwig-Maximilians-University Munich'
    address: |
      Department of Statistics
      Statistical Learning and Data Science group
    # To add another line, use \AND at the end of the previous one as above
  - name: Michel Lang
    affiliation: TU Dortmund University
    address: |
      | Faculty of Statistics
title:
  formatted: "\\pkg{mlr3spatiotempcv}: Spatiotemporal resampling methods for machine learning in R with \\pkg{mlr3}"
  # If you use tex in the formatted title, also supply version without
  plain:     "mlr3spatiotempcv: spatiotemporal resampling methods for machine learning in R with mlr3"
  # For running headers, if needed
  # short:     "\\pkg{foo}: A Capitalized Title"
abstract: >
  The R package [mlr3spatiotempcv](https://mlr3spatiotempcv.mlr-org.com) is an extension package of the machine-learning framework [mlr3](https://mlr3.mlr-org.com).
  It adds support for spatiotemporal resampling methods and their visualization.
  Spatiotemporal resampling methods are needed to assess model performance in a variety of predictive situations in which spatial, temporal, or spatiotemporal autocorrelation is present.
  Cross-validation performance estimates may be biased when this is ignored.
  Currently various R packages implementing different spatiotemporal partitioning strategies exist: sperrorest, blockCV, CAST.
  The goal of [mlr3spatiotempcv](https://mlr3spatiotempcv.mlr-org.com) is to gather the available spatiotemporal resampling methods in R and make them available to users through a simple and common interface.
  This is made possible by integrating the package directly into the [mlr3](https://mlr3.mlr-org.com) machine-learning framework, which already has support for generic non-spatiotemporal resampling methods such as random partitioning.
  This simplifies the step of integrating package-specific syntax into an overarching machine-learning pipeline, making it easier for users to choose from a variety of different spatiotemporal resampling methods.
  The users' decision to use a specfic resampling method should depend on the predictive task at hand, the autocorrelation within the data, and the structure of the sampling design used to collect the data.
keywords:
  formatted: [cross-validation, predictive performance, machine learning, autocorrelation, spatial, temporal, "\\proglang{R}"]
  plain:     [cross-validation, predictive performance, autocorrelation, spatial, temporal, R]
preamble: >
  \usepackage{amsmath}
  \usepackage{amssymb}
  \usepackage{booktabs}
  \usepackage{longtable}
  \usepackage{adjustbox}
  \usepackage{multirow}
  \usepackage{tabularx}
  \usepackage{placeins}
  \usepackage{scrextend}
  \usepackage{tablefootnote}
  \newcommand{\specialcell}[2][l]{%
    \begin{tabular}[#1]{@{}l@{}}#2\end{tabular}}
tables: true
bibliography: paper.bib
output:
  bookdown::pdf_book:
    base_format: rticles::jss_article
    includes:
      in_header: header.tex
---

>>>>

---
documentclass: jss
author:
  - name: Patrick Schratz
    affiliation: 'Friedrich Schiller University Jena'
    # affiliaton2: 'Ludwig-Maximilians-University Munich'
    # use this syntax to add text on several lines
    # must use German name, see https://www.lmu.de/de/die-lmu/struktur/zentrale-universitaetsverwaltung/kommunikation-und-presse/lmu-brand-guide/content-style-guide/index.html
    address: |
      | Department of Geography
      | Geographic Information Science group
    email: \email{patrick.schratz@uni-jena.de}
  - name: Alexander Brenning
    affiliation: 'Friedrich Schiller University Jena \AND'
    address: |
      | Department of Geography
      | Geographic Information Science group
    email: \email{alexander.brenning@uni-jena.de}
  - name: Marc Becker
    affiliation: 'Ludwig-Maximilians-Universität München'
    address: |
      | Department of Statistics
      | Statistical Learning and Data Science group
    # To add another line, use \AND at the end of the previous one as above
  - name: Michel Lang
    affiliation: TU Dortmund University
    address: |
      | Faculty of Statistics
title:
  formatted: "\\pkg{mlr3spatiotempcv}: Spatiotemporal resampling methods for machine learning in R with \\pkg{mlr3}"
  # If you use tex in the formatted title, also supply version without
  plain:     "mlr3spatiotempcv: spatiotemporal resampling methods for machine learning in R with mlr3"
  # For running headers, if needed
  # short:     "\\pkg{foo}: A Capitalized Title"
abstract: >
  The R package [mlr3spatiotempcv](https://mlr3spatiotempcv.mlr-org.com) is an extension package of the machine-learning framework [mlr3](https://mlr3.mlr-org.com).
  It adds support for spatiotemporal resampling methods and their visualization.
  Spatiotemporal resampling methods are needed to assess model performance in a variety of predictive situations in which spatial, temporal, or spatiotemporal autocorrelation is present.
  Cross-validation performance estimates may be biased when this is ignored.
  Currently various R packages implementing different spatiotemporal partitioning strategies exist: sperrorest, blockCV, CAST.
  The goal of [mlr3spatiotempcv](https://mlr3spatiotempcv.mlr-org.com) is to gather the available spatiotemporal resampling methods in R and make them available to users through a simple and common interface.
  This is made possible by integrating the package directly into the [mlr3](https://mlr3.mlr-org.com) machine-learning framework, which already has support for generic non-spatiotemporal resampling methods such as random partitioning.
  This simplifies the step of integrating package-specific syntax into an overarching machine-learning pipeline, making it easier for users to choose from a variety of different spatiotemporal resampling methods.
  The users' decision to use a specfic resampling method should depend on the predictive task at hand, the autocorrelation within the data, and the structure of the sampling design used to collect the data.
keywords:
  formatted: [cross-validation, predictive performance, machine learning, autocorrelation, spatial, temporal, "\\proglang{R}"]
  plain:     [cross-validation, predictive performance, autocorrelation, spatial, temporal, R]
preamble: >
  \usepackage{amsmath}
  \usepackage{amssymb}
  \usepackage{booktabs}
  \usepackage{longtable}
  \usepackage{adjustbox}
  \usepackage{multirow}
  \usepackage{tabularx}
  \usepackage{placeins}
  \usepackage{scrextend}
  \usepackage{tablefootnote}
  \newcommand{\specialcell}[2][l]{%
    \begin{tabular}[#1]{@{}l@{}}#2\end{tabular}}
tables: true
bibliography: paper.bib
output:
  bookdown::pdf_book:
    base_format: rticles::jss_article
    includes:
      in_header: header.tex
---
